Assignment 4

### 2015-03-10 rmtw/a4/latex8.tex
Added Hyp3 stuff

>>>>

\SubSection{Test Used for H\textsubscript{fault}}
The frequency of A, B and C faults found were tabularised against the groups which found them. An example of this is found in table 3. In order to determine if they do find the same faults, a Chi-Square test of independence was performed on the tabulated results.

\begin{table}
	\centering
	\begin{tabular}[Ht]{| l | l | l | l |}
	\hline
	 & A Faults & B Faults & C Faults  \\
	\hline
	Group A & 36 & 40 & 35 \\
	\hline
	Group B & 31 & 47 & 28 \\
	\hline
	\end{tabular}
	\caption{Fault counts of risk type per group}
\end{table}
